\normalfont\spacedallcaps{Marvel Graph Database}

### 2022-01-21 report/main.tex
report

\title{\normalfont\spacedallcaps{Article Title}} % The article title

@@

  \includegraphics[scale=0.5]{plot_relazioni.png}

@@

  \includegraphics[scale=0.5]{plot_corrispondenza_personaggi.png}

@@

  \includegraphics[scale=0.5]{plot_descrizione_fumetti.png}

@@

\renewcommand{\refname}{\spacedlowsmallcaps{References}} % For modifying the bibliography heading

\bibliographystyle{unsrt}

\bibliography{sample.bib} % The file containing the bibliography

>>>>

\title{\normalfont\spacedallcaps{Marvel Graph Database}} % The article title

@@

  \includegraphics[scale=0.5]{./Figures/plot_relazioni.png}

@@

  \includegraphics[scale=0.5]{./Figures/plot_corrispondenza_personaggi.png}

@@

  \includegraphics[scale=0.5]{./Figures/plot_descrizione_fumetti.png}

@@

\printbibliography %Prints bibliography
